### 2015-06-16 writing/S'15 LSTM/data.tex
Longer example.
Final clarifications.

\begin{table}[tp]
  \centering\small
%  \begin{subtable}[t]{0.45\textwidth}
%    \centering
%    \begin{tabular}[t]{l l}
%      \toprule
%      Formula     & Interpretation \\
%      \midrule
%      $p_1$, $p_2$, $p_3$, $p_4$, $p_5$, $p_6$ & $\sem{x} \in \{\True, \False\}$ \\
%      $\plneg \varphi$ & $\True$ iff $\sem{\varphi} = \False$ \\
%      $(\varphi \pland \psi)$ & $\True$ iff $\False \notin \{\sem{\varphi}, \sem{\psi}\}$ \\
%      $(\varphi \plor \psi)$  & $\True$ iff $\True \in \{\sem{\varphi}, \sem{\psi}\}$ \\
%      \bottomrule
%    \end{tabular}    
%    \caption{Well-formed formulae. $\varphi$ and $\psi$
%      range over all well-formed formulae, and $\sem{\cdot}$ is
%      the interpretation function mapping formulae into $\{\True,
%      \False\}$.}\label{tab:pl}
%  \end{subtable}
    \begin{tabular}[t]{r c l}
      \toprule
      $\plneg p_3$        & $\natneg$ & $p_3$ \\
%      $\plneg \plneg p_6$ & $\nateq$  & $p_6$ \\
      $p_3$               & $\natfor$ & $(p_3 \plor p_2)$ \\
      $(p_1 \plor (p_2 \plor p_4))$               & $\natrev$ & $(p_2 \pland  \plneg p_4)$ \\
      %$(a \natfor b)$   & $\nateq$  & $(b \natrev a)$ \\	
      $\plneg\, (\plneg p_1 \pland \plneg p_2)$ & $\nateq$ & $(p_1 \plor p_2)$ \\ 
      $(p_3 \pland \plneg p_1 ) \plor \plneg p_3$    & $\natrev$& $\plneg\, (p_3 \plor p_2)$ \\
      %<	( not ( c ( or b ) ) )	( ( c ( and ( not a ) ) ) ( or ( not c ) ) )
      \bottomrule
    \end{tabular}
    \caption{Examples of short expressions from the artificial data introduced by \protect\citealt{Bowman:Potts:Manning:2014}. For brevity, we only show the parentheses that are needed to disambiguate the sentences rather than the full binary bracketings.}\label{tab:plexs}
\end{table}

@@

\paragraph{The corpus}
The sentence pairs in the corpus are divided into thirteen bins according to the number of logical connectives (\word{and, or, not}) in the longer of the two sentences in the pair. We test the model on each bin separately (58k total examples, using an 80/20\% train/test split) in order to evaluate how its performance depends on the complexity of the sentences. In three experiments, we train our models on the training portions of bins 0--3 (62k examples), 0--4 (90k), and 0--6 (160k), and test on every bin but the trivial bin 0. Capping the size of the training sentences allows us to evaluate how the models interpret the sentences: if their performance falls off abruptly above the cutoff, it is reasonable to assume that the models are depending heavily on specific sentence structures, and cannot generalize to new structures. If their performance decays gradually\footnote{Since sentences are fixed-dimensional vectors of fixed-precision floating point numbers, all models will make errors on sentences above some length, and L2 regularization (which helps overall performance) exacerbates this by preventing the model from using the kind of numerically precise, nonlinearity-saturating functions that would generalize best.} with no such abrupt change, then it must have learned a more generally valid interpretation function for the language which respects its recursive structure.

>>>>

\begin{table}[tp]
  \centering\small
%  \begin{subtable}[t]{0.45\textwidth}
%    \centering
%    \begin{tabular}[t]{l l}
%      \toprule
%      Formula     & Interpretation \\
%      \midrule
%      $p_1$, $p_2$, $p_3$, $p_4$, $p_5$, $p_6$ & $\sem{x} \in \{\True, \False\}$ \\
%      $\plneg \varphi$ & $\True$ iff $\sem{\varphi} = \False$ \\
%      $(\varphi \pland \psi)$ & $\True$ iff $\False \notin \{\sem{\varphi}, \sem{\psi}\}$ \\
%      $(\varphi \plor \psi)$  & $\True$ iff $\True \in \{\sem{\varphi}, \sem{\psi}\}$ \\
%      \bottomrule
%    \end{tabular}    
%    \caption{Well-formed formulae. $\varphi$ and $\psi$
%      range over all well-formed formulae, and $\sem{\cdot}$ is
%      the interpretation function mapping formulae into $\{\True,
%      \False\}$.}\label{tab:pl}
%  \end{subtable}
    \begin{tabular}[t]{r c l}
      \toprule
      $\plneg p_3$        & $\natneg$ & $p_3$ \\
%      $\plneg \plneg p_6$ & $\nateq$  & $p_6$ \\
      $p_3$               & $\natfor$ & $p_3 \plor p_2$ \\
%      $p_1 \plor (p_2 \plor p_4)$               & $\natrev$ & $p_2 \pland  \plneg p_4$ \\
      $(\plneg p_2) \pland p_6  $ & $\natalt$ & $     \plneg ( p_6 \plor ( p_5 \plor p_3 ) ) $\\
      %$(a \natfor b)$   & $\nateq$  & $(b \natrev a)$ \\	
 $    p_4 \plor ( \plneg ( ( p_1   $ & $ \natfor $ & $  \plneg ( ( ( ( \plneg p_6 ) \plor ( \plneg p_4 ) )   $\\      
$ \plor p_6 )  \plor p_4 ) )$ &&$ \pland ( \plneg p_5 ) )\pland ( p_6 \pland p_6 ) ) $\\
% $(p_3 \pland \plneg p_1 ) \plor \plneg p_3$    & $\natrev$& $\plneg\, (p_3 \plor p_2)$ \\
      %<	( not ( c ( or b ) ) )	( ( c ( and ( not a ) ) ) ( or ( not c ) ) )
      \bottomrule
    \end{tabular}
    \caption{Examples of short to moderate length pairs from the artificial data introduced by \protect\citealt{Bowman:Potts:Manning:2014}. For brevity, we only show the parentheses that are needed to disambiguate the sentences rather than the full binary bracketings.}\label{tab:plexs}
\end{table}

@@

\paragraph{The corpus}
The sentence pairs in the corpus are divided into thirteen bins according to the number of logical connectives (\word{and, or, not}) in the longer of the two sentences in the pair. We test the model on each bin separately (58k total examples, using an 80/20\% train/test split) in order to evaluate how its performance depends on the complexity of the sentences. In three experiments, we train our models on the training portions of bins 0--3 (62k examples), 0--4 (90k), and 0--6 (160k), and test on every bin but the trivial bin 0. Capping the size of the training sentences allows us to evaluate how the models interpret the sentences: if their performance falls off abruptly above the cutoff, it is reasonable to assume that the models are depending heavily on specific sentence structures, and cannot generalize to new structures. If their performance decays gradually\footnote{Since sentences are fixed-dimensional vectors of fixed-precision floating point numbers, all models will make errors on sentences above some length, and L2 regularization (which helps overall performance) exacerbates this by discouraging the model from using the kind of numerically precise, nonlinearity-saturating functions that generalize best.} with no such abrupt change, then it must have learned a more generally valid interpretation function for the language which respects its recursive structure.

### 2015-06-16 writing/S'15 LSTM/figure1.tex
Delete SAT instances; logging; paper push.
Learning curve
Paper submission candidate.
Final clarifications.

\begin{subfigure}[t]{0.45\textwidth}
\centering
\scalebox{0.75}{
 \begin{tikzpicture}
    \def\dx{21pt}
    \def\dy{27pt}

@@

     \caption{The architecture for the tree-structured sentence models. Terminal nodes are learned embeddings and nonterminal nodes are NN or NTN layers.}\label{fig:model:tree}

@@

\begin{subfigure}[t]{0.45\textwidth}
  \centering
\scalebox{0.75}{
 \begin{tikzpicture}
    \def\dx{35pt}
    \def\dy{27pt}

@@

   \caption{The architecture for the LSTM sentence model. Nodes in the lower row are learned embeddings and nodes on the upper row are LSTM units.}\label{fig:model:seq}

>>>>

\begin{subfigure}[t]{0.45\textwidth}
\centering
\scalebox{0.72}{
 \begin{tikzpicture}
    \def\dx{21pt}
    \def\dy{27pt}

@@

     \caption{The architecture for the tree-structured sentence models. Terminal nodes are learned embeddings and nonterminal nodes are NN, NTN, or TreeLSTM layers.}\label{fig:model:tree}

@@

\begin{subfigure}[t]{0.45\textwidth}
  \centering
\scalebox{0.72}{
 \begin{tikzpicture}
    \def\dx{35pt}
    \def\dy{27pt}

@@

   \caption{The architecture for the sequence sentence model. Nodes in the lower row are learned embeddings and nodes on the upper row are LSTM layers.}\label{fig:model:seq}
